\section{Unified System Design}
Just as a painting would not look right if painted by multiply artists, a system would not work right if designed by multiple architects.  Brooks claims that ``conceptual integrity'' is the most important consideration in system design, and that it is better for a system to reflect on set of design ideas rather than many good, uncoordinated ideas.

The ultimate test of system design, Brooks says, is the ratio of function to conceptual complexity.  Function means being able to do complicated things quickly, conceptual complexity is how difficult it is to master.  Neither high function nor low complexity is enough by themselves.

There are two fundamental levels to any system, the architecture and implementation.  A careful separation of these two things will aid in the creation of a unified design while allowing for partitioning.  While the architecture must be created by one person, or a small group of agreeable people, implementation is more free, and so it can be separated into large groups.  Architecture says what happens while implementation says how it happens.  It is important that architecture is consistent because it is ``user facing'' meaning it is the only part that the consumer interacts with.  The implementation may change vastly while the architecture remains the same at no cost to the user.

Communication, as in any organization, plays an extremely important role for software engineers.  It is required not only for development and communication between teams, but for communication to the user in the form of a manual.  Because manuals must be precise, formal definitions and feature descriptions are required to avoid confusion.  One must be careful however to maintain separation of architecture and implementation -- while stating the implementation of a feature would be a valid definition, this would cross the boundary and therefore be uncalled for even being more precise.

Meetings are of course necessary.  Brooks suggests weekly half-day meetings where representatives of the hardware and software implementers, as well as market planners can propose problems or changes, and discuss possible solutions.  The other type of meeting suggested is a yearly two-week long meeting designed to empty the backlog of issues which where initially rejected at the weekly meetings but have caused issues since.
